---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# reservetestr

The goal of reservetestr is to provide a framework for testing loss reserve methods. Specifically, an interface to test methods against the [Casualty Actuarial Society (CAS) Loss Reserve Database](http://www.casact.org/research/index.cfm?fa=loss_reserves_data) is provided.

## Installation

You can install reservetestr from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("problemofpoints/reservetestr")
```

## Example Useage

Insert example here...

```{r example-1}

```

## Future Enhancements

- [ ] write function to apply reserving methods
  - start with deterministic? then stochastic? 
    - different functions or argument?
  - make resulting object an S3 class? 
  - use CL/Mack as test (use as vignette)
  - add more error handling
- [ ] write wrappers around methods to work with above function
  - do for as many methods as possible included in `ChainLadder` package
  - for deterministic, do average of methods example?
  - add more error handling
- [ ] write functions to create exhibits

