---
title: "Back-testing the Mack Method"
author: "Adam Troyer"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Back-testing the Mack Method}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(reservetestr)
suppressPackageStartupMessages(library(ChainLadder))
library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)


ggSetTheme()

```

This vignette shows how to use the `reservetestr` package to back-test the Mack Method on the CAS Loss Reserve database. 

## CAS Loss Reserve Database

From the [CAS website](http://www.casact.org/research/index.cfm?fa=loss_reserves_data):

> "Our goal is to prepare a clean and nice data set of loss triangles that could be used for claims reserving studies.
The data includes major personal and commercial lines of business from U.S. property casualty insurers.
The claims data comes from Schedule P - Analysis of Losses and Loss Expenses
in the National Association of Insurance Commissioners (NAIC) database."

Below is an example paid loss triangle from the database. The first triangle is the upper triangle used to fit the model. The second triangle is the actual lower right of the triangle used for model validation / testing.

```{r sample-data-train, fig.cap="Sampe Paid Loss Triangle - Training data"}
cas_loss_reserve_db %>%
  get_meyers_subset() %>%
  filter(line == "ppauto" & group_id == 388) %>%
  pluck("train_tri_set", 1, "paid")
```

```{r sample-data-test, fig.cap="Sampe Paid Loss Triangle - Testing data"}
cas_loss_reserve_db %>%
  get_meyers_subset() %>%
  filter(line == "ppauto" & group_id == 388) %>%
  pluck("test_tri_set", 1, "paid")
```

The back-testing results use a subset of the full database, resulting in 50 triangles across four lines of business - comauto, othliab, ppauto, wkcomp.

```{r subset-data, fig.cap="Summary of Triangles by Line"}
cas_db_subset <- cas_loss_reserve_db %>%
  get_meyers_subset()

cas_db_subset %>%
  group_by(line) %>%
  summarise(`# of Companies` = n()) %>%
  knitr::kable()
```

## Back-testing

Now we can run the Mack method on our triangle training data and back-test its accuracy. We use the implementation of the Mack method in the `ChainLadder` package, `MackChainLadder`, applied to the `comauto` line of business.


```{r backtest-mack, warning=FALSE, message=FALSE, echo=FALSE}

mack_paid_results <- run_single_backtest(cas_db_subset, 
                                         testr_MackChainLadder, 
                                         lines_to_include = "comauto",
                                         loss_type_to_backtest = "paid", 
                                         method_label = "mack_paid")

```

The output provided is the below. 

```{r mack-glimpse}

glimpse(mack_paid_results)

```

We can create a p-p plot to visually access the accuracy of our estimates.

```{r mack-exhibits-pp}

create_pp_plot(mack_paid_results, by_line = TRUE)

```


```{r mack-exhibits-histogram}

create_histogram_plot(mack_paid_results, by_line = TRUE, bin_number = 10)

```


- add BootChainLadder 
- add GLMReserve
- build deck

